Simulating cosmic variance in Weak Lensing: effects on parameter inferences

### 2015-12-04 Paper/paper.tex
modified label of Fig3 and legend of Fig4

\begin{figure}
\includegraphics[scale=0.3]{Figures/scaling_nr.eps}
\caption{Bias in the $w$ variance, $\langle\h{\sigma}^2_w\rangle$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}). Results for different mock ensembles generated with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple) are shown. The figure shows both the measured trends (solid lines) and their best fits according to equation (\ref{ourscaling}). The thick black line correspond to an ensemble generated with $N_s=1$ and $10^5$ mock realizations. }
\label{wvar_nr}
\end{figure}

@@

\begin{table*}
\begin{center}
\begin{tabular}{ccccc}
\toprule
\textbf{Feature} &  \textbf{Specifications} & $N_b$ &  \textbf{Symbol} & \textbf{Color} \\ \hline \hline
\midrule
Power Spectrum, log binning  & $l \in [100,800] $ & 8 & $\times$ & black  \\ 
Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\times$ & black  \\ 
Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
Power Spectrum, linear binning  & $l \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
Power Spectrum, linear binning  & $l \in [2500,4500] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
Power Spectrum, linear binning  & $l \in [100,4500] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\ 
Power Spectrum, linear binning  & $l \in [100,6000] $ & 39 & \textcolor{blue}{$\bullet$} & \textcolor{blue}{blue}  \\ \hline
Low peaks  & $\kappa_0 \in [-0.06,0.09] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
Intermediate peaks  & $\kappa_0 \in [0.1,0.27] $ & 15 & \textcolor{red}{$\bigstar$} & \textcolor{red}{red}  \\ 
High peaks  & $\kappa_0 \in [0.28,0.45] $ & 15 & \textcolor{red}{$\diamond$} & \textcolor{red}{red}  \\
Low+Intermediate peaks  & $\kappa_0 \in [-0.06,0.27] $ & 30 & \textcolor{OliveGreen}{$\times$} & \textcolor{OliveGreen}{green}  \\
Intermediate+High peaks  & $\kappa_0 \in [0.1,0.45] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\
All peaks  & $\kappa_0 \in [-0.06,0.45] $ & 45 & \textcolor{magenta}{$\blacksquare$} & \textcolor{magenta}{magenta}  \\ \hline
\bottomrule
\end{tabular}
\end{center}
\caption{Catalog of feature types used in this work, along with the chosen number of bands $N_b$ and the plot legends for Figure \ref{curvingnb}.}
\label{featuretable}
\end{table*}

>>>>

\begin{figure}
\includegraphics[scale=0.3]{Figures/scaling_nr.eps}
\caption{Bias in the $w$ variance, $\langle\h{\sigma}^2_w\rangle-\sigma^2_{w,\infty}$, as a function of the number of mock realizations $N_r$ used in the feature covariance estimator (\ref{covest}). Results for different mock ensembles generated with $N_s=$1 (black), 2 (blue), 5 (green), 50 (red), 100 (purple) are shown. The figure shows both the measured trends (solid lines) and their best fits according to equation (\ref{ourscaling}). The thick black line correspond to an ensemble generated with $N_s=1$ and $10^5$ mock realizations. }
\label{wvar_nr}
\end{figure}

@@

\begin{table*}
\begin{center}
\begin{tabular}{ccccc}
\toprule
\textbf{Feature} &  \textbf{Specifications} & $N_b$ &  \textbf{Symbol} & \textbf{Color} \\ \hline \hline
\midrule
Power Spectrum, log binning  & $l \in [100,800] $ & 8 & $\times$ & black  \\ 
Power Spectrum, log binning  & $l \in [1000,6000] $ & 7 & $\blacksquare$ & black  \\ 
Power Spectrum, log binning  & $l \in [100,6000] $ & 15 & \textcolor{red}{$\bullet$} & \textcolor{red}{red}  \\
Power Spectrum, linear binning  & $l \in [100,2000] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
Power Spectrum, linear binning  & $l \in [2500,4500] $ & 15 & \textcolor{red}{$\times$} & \textcolor{red}{red}  \\
Power Spectrum, linear binning  & $l \in [100,4500] $ & 30 & \textcolor{OliveGreen}{$\bullet$} & \textcolor{OliveGreen}{green}  \\ 
Power Spectrum, linear binning  & $l \in [100,6000] $ & 39 & \textcolor{blue}{$\bullet$} & \textcolor{blue}{blue}  \\ \hline
Low peaks  & $\kappa_0 \in [-0.06,0.09] $ & 15 & \textcolor{red}{$+$} & \textcolor{red}{red}  \\ 
Intermediate peaks  & $\kappa_0 \in [0.1,0.27] $ & 15 & \textcolor{red}{$\bigstar$} & \textcolor{red}{red}  \\ 
High peaks  & $\kappa_0 \in [0.28,0.45] $ & 15 & \textcolor{red}{$\diamond$} & \textcolor{red}{red}  \\
Low+Intermediate peaks  & $\kappa_0 \in [-0.06,0.27] $ & 30 & \textcolor{OliveGreen}{$\times$} & \textcolor{OliveGreen}{green}  \\
Intermediate+High peaks  & $\kappa_0 \in [0.1,0.45] $ & 30 & \textcolor{OliveGreen}{$\blacksquare$} & \textcolor{OliveGreen}{green}  \\
All peaks  & $\kappa_0 \in [-0.06,0.45] $ & 45 & \textcolor{magenta}{$\blacksquare$} & \textcolor{magenta}{magenta}  \\ \hline
\bottomrule
\end{tabular}
\end{center}
\caption{Catalog of feature types used in this work, along with the chosen number of bands $N_b$ and the plot legends for Figure \ref{curvingnb}.}
\label{featuretable}
\end{table*}
